Development of User-Friendly\\System Identification Techniques

### 2016-07-15 ch02-qlogms/excitation-design.tex
Use B5 format
Some minor formatting things

\chapter{Design of Excitation Signals}
\label{sec:excitation}
\def\thisDir{ch02-qlogms}
\tikzsetfigurename{ch02fig}
\glsresetall
\myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
\researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM}

@@

\section{Simulations} \label{sec:excitation:simulation}
In the following set of simulations, we will study how the \gls{FRF} of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from \secref{sec:excitation:multisine}.
  \subsection{Setup}
  We consider second-order systems with an equal damping and with resonance frequencies $4$, $8$, $20$, $40$, $80$, $200$, $400$, $800$, $2000$ and $4000 \unit{Hz}$.
  Using the \MATLAB\ instruction \texttt{cheby1}, discrete-time equivalents of these systems are generated.
  These can be represented by a transfer function of the form:
  \begin{equation}
    G \left( z \right)\Big|_{\damping, \fR} =
       \frac{         b_2  z^{2} + b_1 z + b_0}%
            {\phantom{a_2} z^{2} + a_1 z + a_0}
  \text{.}
  \label{eq:excitation:secondOrderSystemDTidentifiable}
  \end{equation}

  This form can also be obtained by applying Tustin's method or bilinear transform~\citep{Oppenheim1996} to the continuous time system \eqref{eq:excitation:secondOrdersub-system}.

@@

    \begin{table}[bt]
      \centering
      \caption{Poles of the initial model of the \bruelkjaer{} 1613 filter with center frequency $\wc$.}
      \label{tbl:excitation:bk1613:poles}
      \begin{tabular}{rrrr}
        \toprule
        \textsc{Pole pair} & \textsc{Damping ($\damping$)} & \textsc{Frequency ($\wn$)} & \textsc{Time constant ($\timeconst$)}\\
        \midrule
        $-(0.067 \pm 0.733j)\,\wc$ & $0.091$ & $0.74\,\wc$ & $15.0\,\wc^{-1}$\\ 
        $-(0.190 \pm 0.982j)\,\wc$ & $0.190$ & $\wc$ & $5.3\, \wc^{-1}$\\ 
        $-(0.123 \pm 1.350j)\,\wc$ & $0.091$ & $1.36\,\wc$ & $8.1 \,\wc^{-1}$\\ 
        \bottomrule
      \end{tabular}
    \end{table}

>>>>

\chapter{Design of Excitation Signals}
\label{sec:excitation}
\chapterBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM}
\def\thisDir{ch02-qlogms}
\tikzsetfigurename{ch02fig}
\glsresetall{}
\myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}

@@

\section{Simulations} \label{sec:excitation:simulation}
In the following set of simulations, we will study how the \gls{FRF} of different second order systems with equal damping (and the corresponding uncertainty) are measured by the multisine excitation signals from \secref{sec:excitation:multisine}.
  \subsection{Setup}
  We consider second-order systems with an equal damping and with resonance frequencies $4$, $8$, $20$, $40$, $80$, $200$, $400$, $800$, $2000$ and $4000 \unit{Hz}$.
  Using the \MATLAB\ instruction \texttt{cheby1}, discrete-time equivalents of these systems are generated.
  These can be represented by a transfer function of the form:
  \begin{equation}
    G \left( z \right)\Big|_{\damping, \fR} =
       \frac{         b_2  z^{2} + b_1 z + b_0}%
            {\phantom{a_2} z^{2} + a_1 z + a_0}
  \text{.}
  \label{eq:excitation:secondOrderSystemDTidentifiable}
  \end{equation}
  This form can also be obtained by applying Tustin's method or bilinear transform~\citep{Oppenheim1996} to the continuous time system \eqref{eq:excitation:secondOrdersub-system}.

@@

    \begin{table}[bt]
      \centering
      \caption{Poles of the initial model of the \bruelkjaer{} 1613 filter around $\wc$.}
      \label{tbl:excitation:bk1613:poles}
      \begin{tabular}{rrrr}
        \toprule
        \textsc{Pole pair} & \textsc{Damping ($\damping$)} & \textsc{Frequency ($\wn$)} & \textsc{Time constant ($\timeconst$)}\\
        \midrule
        $-(0.067 \pm 0.733j)\,\wc$ & $0.091$ & $0.74\,\wc$ & $15.0\,\wc^{-1}$\\ 
        $-(0.190 \pm 0.982j)\,\wc$ & $0.190$ & $\wc$ & $5.3\, \wc^{-1}$\\ 
        $-(0.123 \pm 1.350j)\,\wc$ & $0.091$ & $1.36\,\wc$ & $8.1 \,\wc^{-1}$\\ 
        \bottomrule
      \end{tabular}
    \end{table}

### 2016-07-15 front-and-back-matter/summary.inc.tex
Add thumb index
Small changes Conclusions + Summary
Some minor formatting things

\chapter{Summary}
To understand, simulate and control physical systems, good mathematical models are required. 
System identification is a set of powerful tools that distill mathematical models from measurements of the physical world. 
To this end, one has to:
\begin{enumerate}
\item perform experiments to observe the system in a meaningful way,
\item suppress unwanted effects and extract the features of interest from the measurements,
\item fit a model to the measurements.
\end{enumerate}

@@

The final part of the thesis considers the use of FRF smoothers to obtain better initial values to fit parametric models to the measurement data. 
In particular for low signal-to-noise ratios, local modeling or regularization provide a considerable improvements. 
This allows users to obtain better models, even from poor measurements.

>>>>

\chapter{Summary}
\vspace{-2em}
To understand, simulate and control physical systems, good mathematical models are required. 
System identification is a set of powerful tools that distill mathematical models from measurements of the physical world. 
To this end, one has to:
\begin{enumerate}
\vspace{-0.5em}\item perform experiments to observe the system in a meaningful way,
\vspace{-0.5em}\item suppress unwanted effects and extract the features of interest from the measurements,
\vspace{-0.5em}\item fit a model to the measurements.
\end{enumerate}

@@

The final part of the thesis considers the use of FRF smoothers to obtain better initial values to fit parametric models to the measurement data. 
In particular for low signal-to-noise ratios, local modeling or regularization provide considerable improvements. 
This allows users to obtain better models, even from poor measurements.
